Labor Market Income and Substitution Effects Explain Contemporary Natural Selection

### 2020-12-18 why-natural-selection.Rmd
Corrections about changes over time.

@@

Tables \@ref(tab:tbl-siblings-by-period) and
\@ref(tab:tbl-children-by-period) summarize the results. There is no
evidence for changes in selection effects within the parents' generation. In the
respondents' generation, effect sizes were significantly larger in absolute size 
among the later-born for four polygenic scores: cognitive ability, EA2, EA3 and
extraversion. These changes are inconsistent with the intergenerational change, 
where estimated effect sizes were larger among the earlier, parents' generation.
Three scores showed significant changes in sign: alcohol use
(positive to negative); conscientiousness (negative to positive); and
type II diabetes (negative to positive).

>>>>

stopifnot(sum(summary_period$Change_Parents == "Insignificant") == 33)
stopifnot(sum(summary_period$Change_Respondents == "Size increasing") == 4)
stopifnot(sum(summary_period$Change_Respondents == "Change sign") == 1)
stopifnot(sum(summary_period$Change_Respondents == "Insignificant") == 28)
```

@@

Tables \@ref(tab:tbl-siblings-by-period) and
\@ref(tab:tbl-children-by-period) summarize the results. There is no
evidence for changes in selection effects within the parents' generation. In the
respondents' generation, effect sizes were significantly larger in absolute size 
among the later-born for four polygenic scores: cognitive ability, EA2, EA3 and
extraversion. These changes are inconsistent with the intergenerational change, 
where estimated effect sizes were larger among the earlier, parents' generation.
One score, conscientiousness, showed a significant change in sign, from 
negative to positive effects on fertility.
